---
title: "NMDS plots with associated mantel tests - 18S"
author: "Sven"
date: "2/25/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Notes:
It is best to go through each dataset (five fjords/horizontal Long Sound community/ Vertical Long Sound community) one by one. So following the order of this file from start to finish.

#Set up
```{r Load packages}
library(vegan)
library(phyloseq)
library(ggplot2)
library(dplyr)
library(microbiome)
```
##Import files:
```{r Set path}

uzdir <- "My/Path"
otutable_biom_file <- paste("~/Required Files/", "Merged_otu_table_6600.json", sep = "")
map_file <- paste("~/Required Files/", "Modified_mapping_file_18S copy.txt", sep = "")


```
```{r Create phyloseq object}

# Now import the .biom-formatted otu_table-tax_table file.
biom_otu_tax <- import_biom(otutable_biom_file)

# Add sample data to the dataset using merge
bmsd <- import_qiime_sample_data(map_file)
class(bmsd)
dim(bmsd)
sample_data(bmsd)
sample_variables(bmsd)
biom_otu_tax

#Merge into phyloseq format
Fiord_phyloseq <- merge_phyloseq(biom_otu_tax, bmsd)
Fiord_phyloseq
sample_sums(Fiord_phyloseq)

#Save original phyloseq file
Fiord_phyloseq_v = Fiord_phyloseq

#Fix Misslabel
Fiord_phyloseq@sam_data$Sample_Depth[Fiord_phyloseq@sam_data$Sample_Depth == 1] = 0
#Ensure sample depth is seen as a factor for ease of use
sample_data(Fiord_phyloseq)$Sample_Depth<-as.factor(sample_data(Fiord_phyloseq)$Sample_Depth)
```
###Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, function(x) x/10)
sample_sums(Fiord_phyloseq)
```
#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, round)
sample_sums(Fiord_phyloseq)
Fiord_phyloseq = prune_samples(sample_sums(Fiord_phyloseq)>=1, Fiord_phyloseq)
sample_sums(Fiord_phyloseq)
```
Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)
```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq) > 0)
any(taxa_sums(Fiord_phyloseq)== 0)
sum(taxa_sums(Fiord_phyloseq) == 0)
any(taxa_sums(Fiord_phyloseq) > 1)
sum(taxa_sums(Fiord_phyloseq) > 1)
any(taxa_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```
####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq = prune_taxa(taxa_sums(Fiord_phyloseq) > 1, Fiord_phyloseq)
any(sample_sums(Fiord_phyloseq) == 0)
any(sample_sums(Fiord_phyloseq) > 0)
sum(taxa_sums(Fiord_phyloseq) > 0)
any(sample_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```
###Compare sequences per sample or OTU
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq),TRUE), sorted = 1:ntaxa(Fiord_phyloseq), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq),TRUE),sorted = 1:nsamples(Fiord_phyloseq), type = "Samples"))

title = "Total number of reads"

p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```
```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq)
```
```{r Attached OTU ID}
tax_table(Fiord_phyloseq) <- cbind(tax_table(Fiord_phyloseq), OTU=taxa_names(Fiord_phyloseq))
```
```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq) =gsub("D_0__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_1__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_2__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_3__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_4__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_5__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_6__", "", tax_table(Fiord_phyloseq))

```
```{r Subset}
Biolog_phyloseq = Fiord_phyloseq

Biolog_phyloseq@otu_table@.Data = t(as.matrix(Biolog_Metadat_Num[c(2:4,10:44,49,50)]))

#Subset to in/out
Fiord_phyloseq_in_out = subset_samples(Fiord_phyloseq, !Sample_type == "Transverse")

#Subset horizontal community
Fiord_phyloseq_Horonly = subset_samples(Fiord_phyloseq, Sample_type == "Transverse" & !Sample_Depth == "40" & !Sample_Depth == "100" & !Sample_Depth == "200" & !Sample_Depth == "360")

#Subset vertical community
Fiord_phyloseq_Vert = subset_samples(Fiord_phyloseq, !Sample_type == "in" & !Sample_type == "out")
Fiord_phyloseq_Vert = subset_samples(Fiord_phyloseq_Vert, Sample_Site == "L5")
```
```{r Add detail to phyloseq objects}

#Add distance to phyloseq object
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L1", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = 0
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L2", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(5.59)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L3", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(14.3)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L4", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(10.67)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L5", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(8.47)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L6", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(4.73)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L7", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(3.16)
Fiord_phyloseq_Horonly@sam_data[["Distance_from_L1"]][grep("L8", Fiord_phyloseq_Horonly@sam_data[["Sample_Site"]])] = as.numeric(2.47)

```
##Modify files
```{r Add physicochemical parameters to mapping file}

Modified_mapping_file = read.csv("~/Required Files/Modified_mapping_file_18S.csv", row.names = 1)

sample_data(Fiord_phyloseq) = Modified_mapping_file

```
##Subset phyloseq objects
```{r Subset}

#Subset horizontal community
Fiord_phyloseq_Horonly = subset_samples(Fiord_phyloseq, !Depth_m == "40" & !Depth_m == "100" & !Depth_m == "200" & !Depth_m == "360")

#Subset vertical community
Fiord_phyloseq_Vert = subset_samples(Fiord_phyloseq, Layer == "5")
```
##Phylum colour list for consistency
```{r Phylum colour list}
Phylum_colour_list = c(Acidobacteria = "red",
                       Actinobacteria = "green",
                       "Alphaproteobacteria" = "burlywood1",
                       "Alveolata" = "blueviolet",
                       Archaeplastida = "#F8766D",
                       Bacteroidetes = "steelblue",  
                       Chlamydiae = "navy", 
                       Chloroflexi = "grey",
                       Cyanobacteria = "purple", 
                       "Deltaproteobacteria" = "orange",
                       "Discoba" = "darkslategray1",
                       Euryarchaeota = "aquamarine", 
                       "Epsilonproteobacteria" = "darkslateblue",
                       "Excavata" = "#7CAE00",
                       "Gammaproteobacteria" = "dimgray",
                       "Holozoa" = "forestgreen",
                       "Marine Group I" = "gainsboro",
                       Marinimicrobia = "darkseagreen1",
                       Opisthokonta = "magenta", 
                       Parcubacteria = "chocolate2", 
                       Planctomycetes = "wheat", 
                       Proteobacteria = "olivedrab",
                       "Rhizaria" = "goldenrod",
                       Thaumarchaeota = "firebrick", 
                       SAR = "darkred", 
                       "Stramenopiles" = "darkorchid1",
                       "Thermoplasmata" = "tan",
                       Verrucomicrobia = "gold4", 
                       "Rare Taxa (<1%)" = "black")
```
#Horizontal NMDS plot
```{r Make horizontal community NMDS plot}
#Make phyloseq of Transect
Fiord_phyloseq_Transect_Euk = subset_samples(Eukaryota_phyloseq, Depth_m == "0" | Depth_m == "1" |Depth_m == "10")
Fiord_phyloseq_Transect_Euk@sam_data

#Carry out NMDS creation
NMDS.ord_transect_Euk <- ordinate(Fiord_phyloseq_Transect_Euk, method = "NMDS", distance = "bray")
NMDS.ord_transect_Euk

#Ensure plot will work
sample_data(Fiord_phyloseq_Transect_Euk)$Depth_m<-as.factor(sample_data(Fiord_phyloseq_Transect_Euk)$Depth_m)
Sample_site_shape = as.list(c("1" = 0, "2" = 1, "3" = 2, "4" = 5, "5" = 15, "6" = 16, "7" = 17, "8" = 18))

#Plot NMDS
sampleplot_transect_Euk = plot_ordination(Fiord_phyloseq_Transect_Euk, NMDS.ord_transect_Euk, color = "Depth_m", label = "Distance") +
  scale_colour_manual("Sample Depth", values = Depth_colour_list) +
  theme(legend.position = "right")+
  geom_label(label = Fiord_phyloseq_Transect_Euk@sam_data$Distance)

sampleplot_transect_Euk

dev.copy(png,"Beta Diversity transect Eukonly", units = "in", width = 6, height = 5, res = 500)
dev.off()


stressplot(NMDS.ord_transect_Euk)
dev.copy(png,"transect Stressplot Eukonly", width = 500, height = 350)
dev.off()
NMDS.ord_transect_Euk
```
```{r Export horizontal fjord for later ggarrange}
saveRDS(sampleplot_transect_Euk,"~/Transect_betadiv_18S.rds")
saveRDS(NMDS.ord_transect_Euk,"~/18S_transect_stressplot.rds")
```
#Horizontal community Mantel tests
```{r Set up for horizontal Long Sound community}
#Microbial community distance object
Microbiome.dist_trans = distance(Fiord_phyloseq_Transect, method = "bray", type = "samples")

#Geographical distance objects
Depth.dist_trans = dist(Fiord_phyloseq_Transect@sam_data[,7])
Distance.dist_trans = dist(Fiord_phyloseq_Transect@sam_data[,9])

#Physicochemical parameter distance objects
PP.dist_trans =dist(Fiord_phyloseq_Transect@sam_data[,10:12]) #All three physicochemical parameters
Salinity.dist_trans = dist(Fiord_phyloseq_Transect@sam_data[,10])
Oxygen.dist_trans = dist(Fiord_phyloseq_Transect@sam_data[,12])
Temperature.dist_trans = dist(Fiord_phyloseq_Transect@sam_data[,11])
```
```{r Carry out mantel test for horizontal Long Sound community}
#Geographical mantel test + interactions
mantel(Microbiome.dist_trans, Depth.dist_trans, method = "s", permutations = 999)
mantel(Microbiome.dist_trans, Site.dist_trans, method = "s", permutations = 999)
mantel(Microbiome.dist_trans, Depth.dist_trans + Site.dist_trans, method = "s", permutations = 999)

#Physicochemical parameters
mantel(Microbiome.dist_trans, PP.dist_trans, method = "s", permutations = 999)
mantel(Microbiome.dist_trans, Salinity.dist_trans, method = "s", permutations = 999)
mantel(Microbiome.dist_trans, Oxygen.dist_trans, method = "s", permutations = 999)
mantel(Microbiome.dist_trans, Temperature.dist_trans, method = "s", permutations = 999)

#Geographical + physicochemical - all three physicochemical parameters are known to be in a relationship with depth.
mantel(Microbiome.dist_trans, Depth.dist_trans + Salinity.dist_trans, method = "s", permutations = 999) #Depth and salinity are known to be in a relationship (known as the halocline)
mantel(Microbiome.dist_trans, Depth.dist_trans + Oxygen.dist_trans, method = "s", permutations =  999)
mantel(Microbiome.dist_trans, Depth.dist_trans + Temperature.dist_trans, method = "s", permutations = 999)
8
```
#Horizontal community Anosim tests
```{r Horizontal community Anosim test}
Depth_group = get_variable(Fiord_phyloseq_Transect_Euk, "Depth_m")
Depth_ano = anosim(phyloseq::distance(Fiord_phyloseq_Transect_Euk, "bray"), Depth_group)
Depth_ano$signif
Depth_ano$statistic


```
#Horizontal community Adonis tests
```{r Horizontal community Adonis test}
Depth_group = get_variable(Fiord_phyloseq_Transect_Euk, "Depth_m")
df_tran = as(sample_data(Fiord_phyloseq_Transect_Euk@sam_data), "data.frame")
df_tran.dist = phyloseq::distance(Fiord_phyloseq_Transect_Euk, "bray")
Depth_ado = adonis(df_tran.dist ~ Depth_group)

Depth_ado


```
#Vertical NMDS plot
```{r Make vertical community NMDS plot}

#Isolate eukaryotes
Eukaryota_phyloseq = subset_taxa(Fiord_phyloseq, Domain == "Eukaryota")

#Make phyloseq of profile
Fiord_phyloseq_profile_Euk = subset_samples(Eukaryota_phyloseq, Layer == "5")

Fiord_phyloseq_profile_Euk@sam_data

NMDS.ord_profile_Euk <- ordinate(Fiord_phyloseq_profile_Euk, method = "NMDS", distance = "bray")
NMDS.ord_profile_Euk


sample_data(Fiord_phyloseq_profile_Euk)$Depth_m<-as.factor(sample_data(Fiord_phyloseq_profile_Euk)$Depth_m)

Depth_colour_list = c("0" = "red", "10" = "blue", "40" = "grey", "100" = "green", "200" = "black", "360" = "magenta")

sampleplot_profile_Euk = plot_ordination(Fiord_phyloseq_profile_Euk, NMDS.ord_profile_Euk, color = "Depth_m") +
  scale_colour_manual("Sample Depth", values = Depth_colour_list) +
  theme(legend.position = "right")+
  geom_point(position = position_jitter(h=30,w=30))

sampleplot_profile_Euk

dev.copy(png,"~/Beta Diversity profile Eukonly", units = "in", width = 4, height = 2, res = 500)
dev.off()

stressplot(NMDS.ord_profile_Euk)
dev.copy(png,"Profile Stressplot Eukonly", width = 500, height = 350)
dev.off()
NMDS.ord_profile_Euk

```
```{r Export vertical plots for later ggarrange}
saveRDS(sampleplot_profile_Euk,"~/Profile_betadiv_18S.rds")
saveRDS(NMDS.ord_profile_Euk,"~/18S_profile_stressplot.rds")
```
#Vertical community Mantel tests
```{r Set up for vertical Long Sound community}
#Make microbiome distance object
Microbiome.dist_Pro = distance(Fiord_phyloseq_profile, method = "bray", type = "samples")

#Geographical - depth
View(as.matrix(Fiord_phyloseq_profile@sam_data))
  Depth.dist_Pro = dist(Fiord_phyloseq_profile@sam_data[,7])

#Physicochemical parameters
PP.dist_Pro =dist(Fiord_phyloseq_profile@sam_data[,10:12]) #All three physicochemical parameters
Salinity.dist_Pro = dist(Fiord_phyloseq_profile@sam_data[,10])
Oxygen.dist_Pro = dist(Fiord_phyloseq_profile@sam_data[,12])
Temperature.dist_Pro = dist(Fiord_phyloseq_profile@sam_data[,11])


```
```{r Carry out mantel test for vertical Long Sound community}

#Geographical - depth
mantel(Microbiome.dist_Pro, Depth.dist_Pro, method = "s", permutations = 999)

#Physicochemical parameters
mantel(Microbiome.dist_Pro, PP.dist_Pro, method = "s", permutations = 999)
mantel(Microbiome.dist_Pro, Salinity.dist_Pro, method = "s", permutations = 999)
mantel(Microbiome.dist_Pro, Oxygen.dist_Pro, method = "s", permutations = 999)
mantel(Microbiome.dist_Pro, Temperature.dist_Pro, method = "s", permutations = 999)

```






#vertical community Anosim tests
```{r Horizontal community Anosim test}
Depth_group = get_variable(Fiord_phyloseq_profile_Euk, "Depth_m")
Depth_ano = anosim(phyloseq::distance(Fiord_phyloseq_profile_Euk, "bray"), Depth_group)
Depth_ano$signif
Depth_ano$statistic


```
#Vertical community Adonis tests
```{r Horizontal community Adonis test}
Depth_group = get_variable(Fiord_phyloseq_profile_Euk, "Depth_m")
df_prof = as(sample_data(Fiord_phyloseq_profile_Euk@sam_data), "data.frame")
df_prof.dist = phyloseq::distance(Fiord_phyloseq_profile_Euk, "bray")
Depth_ado = adonis(df_prof.dist ~ Depth_group)

Depth_ado


```