---
title: "α-Diversity and Kruskal Wallis tests"
author: "Sven"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Notes:
It is best to go through each dataset (consensus fjord/horizontal Long Sound community/ Vertical Long Sound community) one by one. So following the order of this file from start to finish, in order.

#Set up
```{r Load packages}
library(vegan)
library(phyloseq)
library(ggplot2)
library(dplyr)
library(microbiome)
```
##Import files:
```{r Import files}

uzdir <- "/Users/sven/Desktop/18S/RStudio_analysis/"

otutable_biom_file <- paste("/Users/sven/Desktop/18S/Rarified_otu_tables_6600/", "Merged_otu_table_6600.json", sep = "")

map_file <- paste("/Users/sven/Desktop/18S/", "18S_2017_map_test.txt", sep = "")


```

```{r Create phyloseq object}

# Now import the .biom-formatted otu_table-tax_table file.
library(phyloseq)
biom_otu_tax <- import_biom(otutable_biom_file)

# Add sample data to the dataset using merge
bmsd <- import_qiime_sample_data(map_file)
class(bmsd)
dim(bmsd)
sample_data(bmsd)
sample_variables(bmsd)
biom_otu_tax


#Merge into phyloseq format
Fiord_phyloseq <- merge_phyloseq(biom_otu_tax, bmsd)
Fiord_phyloseq
sample_sums(Fiord_phyloseq)

#Save original phyloseq file
Fiord_phyloseq_v0 = Fiord_phyloseq

```
##Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, function(x) x/10)
sample_sums(Fiord_phyloseq)
```

#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, round)
sample_sums(Fiord_phyloseq)
Fiord_phyloseq = prune_samples(sample_sums(Fiord_phyloseq)>=1, Fiord_phyloseq)
sample_sums(Fiord_phyloseq)
```

Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)

```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq) > 0)
any(taxa_sums(Fiord_phyloseq)== 0)
sum(taxa_sums(Fiord_phyloseq) == 0)
any(taxa_sums(Fiord_phyloseq) > 1)
sum(taxa_sums(Fiord_phyloseq) > 1)
any(taxa_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```

####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq = prune_taxa(taxa_sums(Fiord_phyloseq) > 1, Fiord_phyloseq)
any(sample_sums(Fiord_phyloseq) == 0)
any(sample_sums(Fiord_phyloseq) > 0)
sum(taxa_sums(Fiord_phyloseq) > 0)
any(sample_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```

##Compare sequences per sample or OTU
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq),TRUE), sorted = 1:ntaxa(Fiord_phyloseq), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq),TRUE),sorted = 1:nsamples(Fiord_phyloseq), type = "Samples"))

title = "Total number of reads"
library(ggplot2)
p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```

```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq)
```

```{r Attached OTU ID}
tax_table(Fiord_phyloseq) <- cbind(tax_table(Fiord_phyloseq), OTU=taxa_names(Fiord_phyloseq))
```

```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq) =gsub("D_0__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_1__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_2__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_3__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_4__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_5__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_6__", "", tax_table(Fiord_phyloseq))

```
##Phylum colour list for consistency
```{r Phylum colour list}
Phylum_colour_list = c(Acidobacteria = "red",
                       Actinobacteria = "green",
                       "Alphaproteobacteria" = "burlywood1",
                       "Alveolata" = "blueviolet",
                       Archaeplastida = "#F8766D",
                       Bacteroidetes = "steelblue",  
                       Chlamydiae = "navy", 
                       Chloroflexi = "grey",
                       Cyanobacteria = "purple", 
                       "Deltaproteobacteria" = "orange",
                       "Discoba" = "darkslategray1",
                       Euryarchaeota = "aquamarine", 
                       "Epsilonproteobacteria" = "darkslateblue",
                       "Excavata" = "#7CAE00",
                       "Gammaproteobacteria" = "dimgray",
                       "Holozoa" = "forestgreen",
                       "Marine Group I" = "gainsboro",
                       Marinimicrobia = "darkseagreen1",
                       Opisthokonta = "magenta", 
                       Parcubacteria = "chocolate2", 
                       Planctomycetes = "wheat", 
                       Proteobacteria = "olivedrab",
                       "Rhizaria" = "goldenrod",
                       Thaumarchaeota = "firebrick", 
                       SAR = "darkred", 
                       "Stramenopiles" = "darkorchid1",
                       "Thermoplasmata" = "tan",
                       Verrucomicrobia = "gold4", 
                       "Rare Taxa (<1%)" = "black")
```
#Subset
```{r Subset}

#Get the 1 m depth to be 0, and say we're treating it as such.
Fiord_phyloseq@sam_data$Depth_m[Fiord_phyloseq@sam_data$Depth_m == 1] = 0

#Add distances to the phyloseq object for accuracy (rather than using stations)
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 1] = 0
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 2] = 5.59
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 3] = 14.3
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 4] = 10.67
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 5] = 8.47
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 6] = 4.73
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 7] = 3.16
Fiord_phyloseq@sam_data$Distance[Fiord_phyloseq@sam_data$Layer == 8] = 2.47

#Isolate Eukaryotes
Eukaryota_phyloseq = subset_taxa(Fiord_phyloseq, Domain == "Eukaryota") 

#Vertical phyloseq object
Fiord_phyloseq_profile_Euk = subset_samples(Eukaryota_phyloseq, Layer == "5")

#Horizontal pyloseq object
Transect_phyloseq_surface = subset_samples(Eukaryota_phyloseq, Depth_m == "0" | Depth_m == "1") #Subset surface community
Transect_phyloseq_10m = subset_samples(Eukaryota_phyloseq, Depth_m == "10") #Subset 10 m community
Transect_phyloseq = merge_phyloseq(Transect_phyloseq_10m, Transect_phyloseq_surface) #Combine horizontal communities
```
```{r Extract just taxa table}
Tax_table_all = as(otu_table(Fiord_phyloseq), "matrix")
if(taxa_are_rows(Fiord_phyloseq)){Tax_table_all <- t(Tax_table_all)} #Transpose if necessary
OTUdf = as.data.frame(Tax_table_all) # Coerce to data.frame
```
#Horizontal community α-diversity plot
```{r Horizontal community plot set up and plotting}

alpha_summary_Hor <- estimate_richness(Transect_phyloseq, measures = c("Observed", "Shannon"))
Evenness_Hor <- evenness(Transect_phyloseq, 'pielou')
alpha_summary_Hor$Pielou <- Evenness_Hor$pielou
#combine with metadata
alpha_meta_Hor <- data.frame(alpha_summary_Hor, sample_data(Transect_phyloseq)
alpha_meta_Hor

#Make plot
Observed_Richness_Hor_D <- ggplot(alpha_meta_Hor, aes(x=Distance, y=Observed)) + 
  geom_point(size=3.5) +
  geom_smooth(method = "lm") +         
  xlab("Distance from the outermost sample (km)") +
 # ggtitle("Sample observed richness separated by depth") +
  labs(y = expression ("Observed Richness")) +
  expand_limits(y=0) +                        
  theme_bw() +
  facet_wrap(~Depth_m) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(axis.title.x = element_text(),
        axis.text.x = element_text(angle=0, colour = "black", hjust = 0.5), 
        axis.text.y = element_text(colour = "black"),
        axis.title.y = element_text(face="bold"),
        plot.title = element_text(hjust=0.5),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black"),
        strip.background = element_rect(colour="black"))
  

Observed_Richness_Hor_D

dev.copy(png, "Transverse_Observed", units = "in", width = 5, height = 4, res = 500)
dev.off()

```
```{r Export Horizontal community for later ggarrange}
saveRDS(Observed_Richness_Hor_D,"~/Desktop/Transect_alphadiv_18S.rds")
```
#Horizontal community Kruskal-Wallis (KW) tests
```{r Carry out horizontal community KW tests}
kruskal.test(Observed ~ Distance, data = alpha_meta_Hor)

#Isolate depths and run for each one individually
alpha_meta_Hor_surface = base::subset(alpha_meta_Hor, Depth_m == "0")

kruskal.test(Observed ~ Distance, data = alpha_meta_Hor_surface)

#Isolate depths and run for each one individually
alpha_meta_Hor_10m = base::subset(alpha_meta_Hor, Depth_m == "10")

kruskal.test(Observed ~ Distance, data = alpha_meta_Hor_10m)

interdepthxdistance<-interaction(alpha_meta_Hor$Depth_m, alpha_meta_Hor$Distance)
KWInt_DepthDistance<-kruskal.test(Observed ~ interdepthxdistance, data = alpha_meta_Hor)
KWInt_DepthDistance

```
#Vertical community α-diversity plot
```{r Vertical community plot set up and plotting}

alpha_summary_Vert <- estimate_richness(Fiord_phyloseq_profile_Euk, measures = c("Observed", "Shannon"))
Evenness_Vert <- evenness(Fiord_phyloseq_profile_Euk, 'pielou')
alpha_summary_Vert$Pielou <- Evenness_Vert$pielou
#combine with metadata
alpha_meta_Vert <- data.frame(alpha_summary_Vert, sample_data(Fiord_phyloseq_profile_Euk))
alpha_meta_Vert

#Make summary
Observed_summary = summarySE(alpha_meta_Vert, "Observed", groupvars = "Depth_m")

#Get the 1 m depth to be 0, and say we're treating it as such.
Observed_Richness_Vert_D <- ggplot(Observed_summary, 
                                   aes(x=as.factor(as.numeric(as.character(Depth_m))), 
                                       y=Observed)) + 
  geom_line(group = "Depth_m")+
  labs(y = expression ("Observed Richness"), x = expression("Sample Depth (m)")) +
  expand_limits(y=0) +                        
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
 # coord_flip()+
 # scale_x_reverse()+
  geom_errorbar(aes(ymin = Observed-se, ymax = Observed + se))

Observed_Richness_Vert_D

dev.copy(png, "Profile_Observed", units = "in", width = 5, height = 4, res = 500)
dev.off()

```
```{r Export Vertical community for later ggarrange}
saveRDS(Observed_Richness_Vert_D,"~/Desktop/Profile_alphadiv_18S.rds")
```
#Vertical community Kruskal-Wallis (KW) tests
```{r Carry out vertical community KW tests}
kruskal.test(Observed ~ Depth_m, data = alpha_meta_Vert)
```


