---
title: "Ggarrange_mrkdwn"
author: "Sven Tobias-Hunefeldt"
date: "1/17/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Notes
It is best to go through each dataset (five fjords/horizontal Long Sound community/ Vertical Long Sound community) one by one. So following the order of this file from start to finish.

#Set up
##Load packages
```{r Load packages}
library(ggplot2)
library(ggpubr)
library(gridGraphics)
library(vegan)

```
##Load objects into environment
```{r Multiple fjords}
#α-diversity
Multifjord_alphaDiv_16S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Multifjord_alphaDiv_16S.rds")

#β-diversity
Multifjord_betadiv_16S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Multifjord_betadiv_16S.rds")

#Community
Multifjord_community_16S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Multifjord_community_16S.rds")
```
```{r Profile}

#No filtering
Domainprofile18S = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Domainprofile18S.rds")
Phylaprofile18S = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylaprofile18S.rds")

#Physicochemical parameters
Profile_CTD_regression = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_CTD_regression.rds")

Profile_alphadiv_16S_Observed.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_alphadiv_16S_Observed.rds")
Profile_alphadiv_16S_Pielou.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_alphadiv_16S_Pielou.rds")

Profile_betadiv_16S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_betadiv_16S.rds")

Phylum_EdgeR_Profile_16S_Depth.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_16S_Depth.rds")
Phylum_EdgeR_Profile_16S_Sal.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_16S_Sal.rds")
Phylum_EdgeR_Profile_16S_Temp.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_16S_Temp.rds")
Phylum_EdgeR_Profile_16S_Ox.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_16S_Ox.rds")

Profile_alphadiv_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_alphadiv_18S.rds")

Profile_betadiv_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Profile_betadiv_18S.rds")

Phylum_EdgeR_Profile_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_18S.rds")
Phylum_EdgeR_Profile_Sal_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Profile_Sal_18S.rds")

```
```{r Transect}
#Physicochemical parameters
Surface_CTD_regression = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/surface_CTD_regression.rds")
D10m_CTD_regression = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/10m_CTD_regression.rds")

Transect_alphadiv_16S_Observed.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Transect_alphadiv_16S_Observed.rds")

Transect_betadiv_16S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Transect_betadiv_16S.rds")

Phylum_EdgeR_Transect_16S_Dist.rds = readRDS("~/Desktop/Fjordpaper/3_Results/Phylum_EdgeR_Transect_16S_Dist.rds")
Phylum_EdgeR_Transect_16S_Sal.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Transect_16S_Sal.rds")
Phylum_EdgeR_Transect_16S_Ox.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Transect_16S_Ox.rds")
Phylum_EdgeR_Transect_16S_Temp.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Transect_16S_Temp.rds")

Transect_alphadiv_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Transect_alphadiv_18S.rds")

Transect_betadiv_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Transect_betadiv_18S.rds")

Phylum_EdgeR_Transect_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Transect_18S.rds")
Phylum_EdgeR_Transect_Sal_18S.rds = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/Phylum_EdgeR_Transect_Sal_18S.rds")
```
```{r Stressplots}
Multi_16S_stressplot = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/16S_Multi_stressplot.rds") #From figure 4
Profile_16S_stressplot = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/16S_Profile_stressplot.rds") #From figure 2
Transect_16S_stressplot = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/16S_Transect_stressplot.rds") # from figure 2

Profile_18S_stressplot = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/18S_Profile_stressplot.rds") #From figure 2
Transect_18S_stressplot = readRDS("~/Desktop/Fjordpaper/3_Results/11_To_ggarrange/18S_Transect_stressplot.rds") # from figure 2

```
#Figure 2 - alpha diveristy
```{r ggarrange figure 2 - α-diversity}

Multifjord_alphaDiv_16S.rds = Multifjord_alphaDiv_16S.rds + 
  ylab("Richness")

Profile_alphadiv_16S_Observed.rds = Profile_alphadiv_16S_Observed.rds + 
  ylab("Richness")

Transect_alphadiv_16S_Observed.rds = Transect_alphadiv_16S_Observed.rds+ 
  ylab("Richness")
          
Profile_alphadiv_16S_Pielou.rds = Profile_alphadiv_16S_Pielou.rds +
  xlab("")+
  ylab("") 

Profile_alphadiv_18S.rds = Profile_alphadiv_18S.rds + 
  xlab("")+
  ylab("")

Transect_alphadiv_18S.rds = Transect_alphadiv_18S.rds+ 
  xlab("")+
  ylab("")
          
          
          
pdf("Alpha_Diversity.pdf")
ggarrange(ggarrange(Transect_alphadiv_16S_Observed.rds, 
          Transect_alphadiv_18S.rds,
          Profile_alphadiv_16S_Observed.rds, 
          Profile_alphadiv_18S.rds,
                              ncol = 2,
                    nrow = 2,
                    labels = c("a",
                   "b",
                   "c",
                   "d"),
          font.label = list(size = 9),
          hjust = 0,
          vjust = 0),
          Multifjord_alphaDiv_16S.rds, 
                    labels = c("","e"),
          font.label = list(size = 9),
          nrow = 2,
          ncol = 1,
          hjust = 0,
          vjust = 0)
dev.off()

```
#Figure 3/4 - beta-diversity
```{r ggarrange figure 3 - β-diversity}

Depth_colour_list = c("0" = "red", "10" = "blue", "40" = "grey", "100" = "green", "200" = "black", "360" = "magenta")

Profile_betadiv_18S.rds = Profile_betadiv_18S.rds + 
  scale_color_manual("Sample Depth (m)", values = Depth_colour_list)

pdf("LongSound_Beta_Diversity_test.pdf", width = 8, height = 6)
ggarrange(Transect_betadiv_16S.rds, 
          Transect_betadiv_18S.rds,
          Profile_betadiv_16S.rds,
          Profile_betadiv_18S.rds,
          legend = F,
          labels = c("a",
                   "b",
                   "c",
                   "d"),
          font.label = list(size = 9),
          hjust = -0.1,
          vjust = 0,
          heights = 2,
          width = 4,
          ncol = 2,
          nrow = 2)
dev.off()

Profile_betadiv_18S.rds
dev.copy(png, "Profile_betadiv_18S", units = "in", res = 500, width = 7, height = 7)
dev.off()

pdf("For legends.pdf", height = 2, width = 4)
Multifjord_betadiv_16S.rds
Transect_betadiv_18S.rds
dev.off()
dev.copy(png, "Multifjord_betadiv_16S", units = "in", res = 500, width = 5, height = 7)
dev.off()
```
```{r ggarrange figure 4 - β-diversity}

pdf("Fivefjord_Diversity.pdf", width = 5, height = 3.34)
Multifjord_betadiv_16S.rds
dev.off()
```
#Supplementary Figure 1
```{r Stressplots}

stressplot(Multi_16S_stressplot) 
Multi_16S_plot = recordPlot()
stressplot(Profile_16S_stressplot)
Profile_16S_plot = recordPlot()
stressplot(Profile_18S_stressplot)
Profile_18S_plot = recordPlot()
stressplot(Transect_16S_stressplot) 
Transect_16S_plot = recordPlot()
stressplot(Transect_18S_stressplot)
Transect_18S_plot = recordPlot()
 


Stress_figure = ggarrange(Transect_16S_plot, 
          Transect_18S_plot,
          Profile_16S_plot,
          Profile_18S_plot,
          Multi_16S_plot,
          labels = c("a",
                   "b",
                   "c",
                   "d",
                   "e"),
          ncol = 3,
          nrow = 2,
          font.label = list(size = 9),
          vjust = 0,
          hjust = -0.1)

Stressfigure = annotate_figure(Stress_figure,
                left = text_grob("Ordination Distance", color = "black", rot = 90),
                bottom = text_grob("Observed Dissimilarity"))

pdf("Stressplots.pdf", width = 9, height = 6)
Stressfigure
dev.off()


```
#Figure Supplemantal Figure 2/5/6/7 - community
```{r Supplementary Figure 2}
Multifjord_community_16S.rds = Multifjord_community_16S.rds + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list)

#Fjord averages
Multifjord_community_16S.rds
dev.copy(png, "Multifjord_community_16S", units = "in", res = 500, width = 7, height = 7)
dev.off()

pdf("Multifjord_community_16S.pdf", height = 3, width = 4)
Multifjord_community_16S.rds
dev.off()
```
```{r Figure Set up}

Domainprofile18S = Domainprofile18S + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylaprofile18S = Phylaprofile18S + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_16S_Depth.rds = Phylum_EdgeR_Profile_16S_Depth.rds + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_16S_Sal.rds = Phylum_EdgeR_Profile_16S_Sal.rds+ 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_16S_Temp.rds = Phylum_EdgeR_Profile_16S_Temp.rds + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_16S_Ox.rds = Phylum_EdgeR_Profile_16S_Ox.rds + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_18S.rds = Phylum_EdgeR_Profile_Sal_18S.rds + 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

Phylum_EdgeR_Profile_Sal_18S.rds = Phylum_EdgeR_Profile_Sal_18S.rds+ 
  theme(axis.title.y = element_blank()) + 
  scale_colour_manual("Phylum", 
                      values = Phylum_colour_list) + 
  xlab("")

```
```{r Figure 5/6}

Phylaprofile18S = Phylaprofile18S + scale_fill_manual(values = Phylum_colour_list)

Figure5 = ggarrange(Domainprofile18S,
          Phylaprofile18S,
          ncol = 2,
          nrow = 1,
          labels = c("a",
                     "b"),
          font.label = list(size = 9),
          hjust = 0,
          vjust = 5,
          legend = F)

Figure5mod =  annotate_figure(Figure5, left = text_grob("Relative Abundance (%)", color = "black", rot = 90), bottom = text_grob("Sample Depth (m)"))
Figure5mod


Figure6 = ggarrange(Profile_CTD_regression, #Post production
                    Profile_CTD_regression,
                    Phylum_EdgeR_Profile_16S_Depth.rds,
                    Phylum_EdgeR_Profile_18S.rds,
                    Phylum_EdgeR_Profile_16S_Sal.rds,
                    Phylum_EdgeR_Profile_Sal_18S.rds,
                    Phylum_EdgeR_Profile_16S_Temp.rds,
                    Phylum_EdgeR_Profile_16S_Ox.rds,
          ncol = 2,
          nrow = 4,
          labels = c("a",
                     "b",
                     "c",
                     "d",
                     "e",
                     "f",
                     "g",
                     "h"),
          font.label = list(size = 9),
          hjust = 0,
          vjust = 0,
          legend = F)
Figure5mod = annotate_figure(Figure6,
                left = text_grob("Relative Abundance (%)", color = "black", rot = 90),
                bottom = text_grob("Sample Depth (m)"))
Figure6mod



pdf("Profile_community_figures_rough.pdf", width = 8, height = 4)
Figure5mod
dev.off()

pdf("Profile_community_figures.pdf")
Figure6mod
dev.off()

ggarrange(Profile_CTD_regression, #Post production
          FALSE,
          Phylum_EdgeR_Profile_16S_Depth.rds,
          Phylum_EdgeR_Profile_18S.rds,
          Phylum_EdgeR_Profile_16S_Sal.rds,
          Phylum_EdgeR_Profile_Sal_18S.rds,
          Phylum_EdgeR_Profile_16S_Temp.rds,
          Phylum_EdgeR_Profile_16S_Ox.rds,
          ncol = 2,
          nrow = 4,
          labels = c("a",
                     "b",
                     "c",
                     "d",
                     "e",
                     "f",
                     "g"),
          legend = T)
dev.copy(png, "For_legend", units = "in", width = 25, height = 35, res = 500)
dev.off()

Profile_CTD_regression
dev.copy(png, "Profile_CTD_regression", width = 7, height = 5, units = "in", res = 500)
dev.off()
```
```{r Figure 7 set up}
Phylum_EdgeR_Transect_16S_Dist.rds = Phylum_EdgeR_Transect_16S_Dist.rds + theme(axis.title.y = element_blank()) + scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")
Phylum_EdgeR_Transect_16S_Sal.rds = Phylum_EdgeR_Transect_16S_Sal.rds + theme(axis.title.y = element_blank())+ scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")
Phylum_EdgeR_Transect_16S_Ox.rds = Phylum_EdgeR_Transect_16S_Ox.rds + theme(axis.title.y = element_blank())+ scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")
Phylum_EdgeR_Transect_16S_Temp.rds = Phylum_EdgeR_Transect_16S_Temp.rds + theme(axis.title.y = element_blank())+ scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")
Phylum_EdgeR_Transect_18S.rds = Phylum_EdgeR_Transect_18S.rds+ theme(axis.title.y = element_blank())+ scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")
Phylum_EdgeR_Transect_Sal_18S.rds = Phylum_EdgeR_Transect_Sal_18S.rds+ theme(axis.title.y = element_blank())+ scale_colour_manual("Phylum", values = Phylum_colour_list)+
  xlab("")+
  ylab("")

```
```{r Figure 7}

Figure7 = ggarrange(Surface_CTD_regression,
          D10m_CTD_regression,
          Phylum_EdgeR_Transect_16S_Dist.rds,
          Phylum_EdgeR_Transect_18S.rds,
          Phylum_EdgeR_Transect_16S_Sal.rds,
          Phylum_EdgeR_Transect_Sal_18S.rds,
          Phylum_EdgeR_Transect_16S_Ox.rds,
         # Emptyplot,
          Phylum_EdgeR_Transect_16S_Temp.rds,
          ncol = 2,
          nrow = 4,
          labels = c("a",
                     "b",
                     "c",
                     "d",
                     "e",
                     "f",
                     "g",
                     "h"),
         font.label = list(size = 9),
         hjust = 0,
         vjust = 1.1,
         legend = F,
         align = "hv",
         common.legend = F)

Figure7mod = annotate_figure(Figure7,
                left = text_grob("Relative Abundance (%)", color = "black", rot = 90),
                bottom = text_grob("Km from outermost sample"))

Figure7mod

pdf("Transect_community_figures.pdf")

Figure7mod

dev.off()

dev.copy(png, "Forlegend_transect", units = "in", height = 25, width = 35, res = 500)
dev.off()

Surface_CTD_regression
dev.copy(png, "Transect_toadd_surface", width = 7, height = 5, units = "in", res = 500)
dev.off()

D10m_CTD_regression
dev.copy(png, "Transect_toadd_10m", width = 7, height = 5, units = "in", res = 500)
dev.off()

pdf("For_legend_2.pdf", height =9, width = 9)
ggarrange(Phylum_EdgeR_Transect_16S_Dist.rds,
          Phylum_EdgeR_Transect_18S.rds,
          Phylum_EdgeR_Transect_16S_Sal.rds,
          Phylum_EdgeR_Transect_Sal_18S.rds,
          Phylum_EdgeR_Transect_16S_Ox.rds,
          Phylum_EdgeR_Transect_16S_Temp.rds,
          ncol = 2,
          nrow = 4,
          legend = T,
          align = "hv")

dev.off()
```

#Phylum colour list
```{r Phylum colour list}

Phylum_colour_list = c(Acidobacteria = "red",
                       Actinobacteria = "green",
                       "Alphaproteobacteria" = "burlywood1",
                       "Alveolata" = "blueviolet",
                       Archaeplastida = "#F8766D",
                       Bacteroidetes = "steelblue",  
                       Chlamydiae = "navy", 
                       Chloroflexi = "grey",
                       Cyanobacteria = "purple", 
                       "Deltaproteobacteria" = "orange",
                       "Discoba" = "darkslategray1",
                       Euryarchaeota = "aquamarine", 
                       "Epsilonproteobacteria" = "darkslateblue",
                       "Excavata" = "#7CAE00",
                       "Gammaproteobacteria" = "dimgray",
                       "Holozoa" = "forestgreen",
                       "Marine Group I" = "gainsboro",
                       Marinimicrobia = "darkseagreen1",
                       Opisthokonta = "magenta", 
                       Parcubacteria = "chocolate2", 
                       Planctomycetes = "wheat", 
                       Proteobacteria = "olivedrab",
                       "Rhizaria" = "goldenrod",
                       Thaumarchaeota = "firebrick", 
                       SAR = "darkred", 
                       "Stramenopiles" = "darkorchid1",
                       "Thermoplasmata" = "tan",
                       Verrucomicrobia = "gold4", 
                       "Rare Taxa (<1%)" = "black")


```
