---
title: "Graphical_Abstract_gitHub"
author: "Sven"
date: "7/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
library(dplyr) - version 0.8.1
library(scales) - version 1.0.0
library(phyloseq) - version 1.26.1
library(ggplot2) - version 3.1.1
library(Rmisc) - version 1.5
##Phylum colour list for consistency
```{r Phylum colour list}
Phylum_colour_list = c(
#Prokaryotes
  Acidobacteria = "#FF6600",
  Actinobacteria = "#FF00FF",
  Bacteroidetes = "#00AAD4",
  Chloroflexi = "#0066FF",
  Euryarchaeota = "#6600FF",
  Gemmatimonadetes = "#FE0066",
  "Marinimicrobia (SAR406 clade)" = "#BC5FD3",
  Planctomycetes = "#AA8800",
  Proteobacteria = "#FF0000",
  Thaumarchaeota = "#8A6F91",
  Verrucomicrobia = "#FFCC00",
  Cyanobacteria = "#330088",
#Eukaryotes  
  Archaeplastida = "#008000",
  Excavata = "#00D400",
  Opisthokonta = "#66FF00",
  SAR = "#2d5016ff"
)
```
#Set up - 16S
library(phyloseq)
```{r Import files}
####Initial env. loading####
setwd("~/My/Path/")
Biolog_Metadat_Num_16S = read.csv("~/My/Path/Biolog_Metadata_Num.csv")
rownames(Biolog_Metadat_Num_16S) = Biolog_Metadat_Num_16S$X
Biolog_Metadat_Num_16S = subset.data.frame(Biolog_Metadat_Num_16S, select = -1)

map_file_16S <- paste("/My/Path/Biolog_Metadata_Num.csv", sep = ",")

bmsd_16S <- import_qiime_sample_data(map_file_16S)

#16S
otutable_biom_file_16S <- paste("/My/Path/", "Merged_otu_table_json.biom", sep = "")

Fiord_phyloseq_16S <- import_biom(otutable_biom_file_16S)
sample_data(Fiord_phyloseq_16S) <- Biolog_Metadat_Num_16S

#Fix Misslabel
Fiord_phyloseq_16S@sam_data$Sample_Depth[Fiord_phyloseq_16S@sam_data$Sample_Depth == 1] = 0

```
##Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq_16S = transform_sample_counts(Fiord_phyloseq_16S, function(x) x/10)
sample_sums(Fiord_phyloseq_16S)
```
#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq_16S = transform_sample_counts(Fiord_phyloseq_16S, round)
sample_sums(Fiord_phyloseq_16S)
Fiord_phyloseq_16S = prune_samples(sample_sums(Fiord_phyloseq_16S)>=1, Fiord_phyloseq_16S)
sample_sums(Fiord_phyloseq_16S)
```
Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)
```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq_16S) > 0)
any(taxa_sums(Fiord_phyloseq_16S)== 0)
sum(taxa_sums(Fiord_phyloseq_16S) == 0)
any(taxa_sums(Fiord_phyloseq_16S) > 1)
sum(taxa_sums(Fiord_phyloseq_16S) > 1)
any(taxa_sums(Fiord_phyloseq_16S) < 1)
sum(taxa_sums(Fiord_phyloseq_16S) < 1)
```
####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq_16S = prune_taxa(taxa_sums(Fiord_phyloseq_16S) > 1, Fiord_phyloseq_16S)
any(sample_sums(Fiord_phyloseq_16S) == 0)
any(sample_sums(Fiord_phyloseq_16S) > 0)
sum(taxa_sums(Fiord_phyloseq_16S) > 0)
any(sample_sums(Fiord_phyloseq_16S) < 1)
sum(taxa_sums(Fiord_phyloseq_16S) < 1)
```
##Compare sequences per sample or OTU
library(ggplot2)
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq_16S),TRUE), sorted = 1:ntaxa(Fiord_phyloseq_16S), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq_16S),TRUE),sorted = 1:nsamples(Fiord_phyloseq_16S), type = "Samples"))

title = "Total number of reads"

p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```
##Check Variables
```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq_16S)
```
```{r Attached OTU ID}
tax_table(Fiord_phyloseq_16S) <- cbind(tax_table(Fiord_phyloseq_16S), OTU=taxa_names(Fiord_phyloseq_16S))
```
##Rename Ranks
```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq_16S)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq_16S) =gsub("D_0__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_1__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_2__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_3__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_4__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_5__", "", tax_table(Fiord_phyloseq_16S))
tax_table(Fiord_phyloseq_16S) =gsub("D_6__", "", tax_table(Fiord_phyloseq_16S))

```
```{r Subset}
#Subset to in/out
Fiord_phyloseq_16S_in_out = subset_samples(Fiord_phyloseq_16S, !Sample_type == "Transverse")

#Subset horizontal community
Fiord_phyloseq_16S_Horonly = subset_samples(Fiord_phyloseq_16S, Sample_type == "Transverse" & !Sample_Depth == "40" & !Sample_Depth == "100" & !Sample_Depth == "200" & !Sample_Depth == "360")

#Subset vertical community
Fiord_phyloseq_16S_Vert = subset_samples(Fiord_phyloseq_16S, !Sample_type == "in" & !Sample_type == "out")
Fiord_phyloseq_16S_Vert = subset_samples(Fiord_phyloseq_16S_Vert, Sample_Site == "L5")
```
```{r Add detail to phyloseq objects}

#Add distance to phyloseq_16S object
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L1", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = 0
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L2", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(5.59)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L3", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(14.3)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L4", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(10.67)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L5", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(8.47)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L6", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(4.73)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L7", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(3.16)
Fiord_phyloseq_16S_Horonly@sam_data[["Distance_from_L1"]][grep("L8", Fiord_phyloseq_16S_Horonly@sam_data[["Sample_Site"]])] = as.numeric(2.47)

```

#Set up - 18S
library(phyloseq)
```{r Import files}
####Initial env. loading####
Biolog_Metadat_Num_18S = read.csv("~/My/Path/18S_2017_map_test.csv")
row.names(Biolog_Metadat_Num_18S) = Biolog_Metadat_Num_18S$SampleID

Biolog_Metadat_Num_18S = subset.data.frame(Biolog_Metadat_Num_18S, select = -1)

map_file_18S = paste("/My/Path/18S_2017_map_test.txt")

bmsd_18S <- import_qiime_sample_data(map_file_18S)


otutable_biom_file_18S <- paste("/My/Path/", "Merged_otu_table_6600.json", sep = "")

#18S
Fiord_phyloseq_18S <- import_biom(otutable_biom_file_18S)
sample_data(Fiord_phyloseq_18S) <- Biolog_Metadat_Num_18S

#Fix Misslabel
#18S
Fiord_phyloseq_18S@sam_data$Depth_m[Fiord_phyloseq_18S@sam_data$Depth_m == 1] = 0

```
##Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq_18S = transform_sample_counts(Fiord_phyloseq_18S, function(x) x/10)
sample_sums(Fiord_phyloseq_18S)
```
#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq_18S = transform_sample_counts(Fiord_phyloseq_18S, round)
sample_sums(Fiord_phyloseq_18S)
Fiord_phyloseq_18S = prune_samples(sample_sums(Fiord_phyloseq_18S)>=1, Fiord_phyloseq_18S)
sample_sums(Fiord_phyloseq_18S)
```
Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)
```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq_18S) > 0)
any(taxa_sums(Fiord_phyloseq_18S)== 0)
sum(taxa_sums(Fiord_phyloseq_18S) == 0)
any(taxa_sums(Fiord_phyloseq_18S) > 1)
sum(taxa_sums(Fiord_phyloseq_18S) > 1)
any(taxa_sums(Fiord_phyloseq_18S) < 1)
sum(taxa_sums(Fiord_phyloseq_18S) < 1)
```
####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq_18S = prune_taxa(taxa_sums(Fiord_phyloseq_18S) > 1, Fiord_phyloseq_18S)
any(sample_sums(Fiord_phyloseq_18S) == 0)
any(sample_sums(Fiord_phyloseq_18S) > 0)
sum(taxa_sums(Fiord_phyloseq_18S) > 0)
any(sample_sums(Fiord_phyloseq_18S) < 1)
sum(taxa_sums(Fiord_phyloseq_18S) < 1)
```
##Compare sequences per sample or OTU
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq_18S),TRUE), sorted = 1:ntaxa(Fiord_phyloseq_18S), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq_18S),TRUE),sorted = 1:nsamples(Fiord_phyloseq_18S), type = "Samples"))

title = "Total number of reads"

p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```
##Check Variables
```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq_18S)
```
```{r Attached OTU ID}
tax_table(Fiord_phyloseq_18S) <- cbind(tax_table(Fiord_phyloseq_18S), OTU=taxa_names(Fiord_phyloseq_18S))
```
##Rename Ranks
```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq_18S)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq_18S) =gsub("D_0__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_1__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_2__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_3__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_4__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_5__", "", tax_table(Fiord_phyloseq_18S))
tax_table(Fiord_phyloseq_18S) =gsub("D_6__", "", tax_table(Fiord_phyloseq_18S))

```
```{r Subset}

#Only Eukaryota
Fiord_phyloseq_18S = subset_taxa(Fiord_phyloseq_18S, Domain == "Eukaryota")

#Subset horizontal community
Fiord_phyloseq_18S_Horonly = subset_samples(Fiord_phyloseq_18S, !Depth_m == "40" & !Depth_m == "100" & !Depth_m == "200" & !Depth_m == "360")

#Subset vertical community
Fiord_phyloseq_18S_Vert = subset_samples(Fiord_phyloseq_18S, Layer == "5")
```
```{r Add detail to phyloseq objects}

#Add distance to phyloseq_18S object
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("1", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = 0
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("2", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(5.59)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("3", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(14.3)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("4", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(10.67)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("5", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(8.47)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("6", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(4.73)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("7", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(3.16)
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("8", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(2.47)

Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("1", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = 0
Fiord_phyloseq_18S_Horonly@sam_data[["Distance_from_L1"]][grep("2", Fiord_phyloseq_18S_Horonly@sam_data[["Layer"]])] = as.numeric(5.59)

```
#Horizontal
##Surface
###0km
```{r Community for 0 km surface}
#Make combined object
Fiord_phyloseq_Horonly = merge_phyloseq(Fiord_phyloseq_16S_Horonly, Fiord_phyloseq_18S_Horonly)

#Subset samples
Comm_0_0m = subset_samples(Fiord_phyloseq_Horonly, Distance_from_L1 == "0" & Sample_Depth == "0" | Distance_from_L1 == "0" & Depth_m == "0")

Comm_0_0m_df = Comm_0_0m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.



#Make Summary plot
Sum_Comm_0_0m_df <- summarySE(Comm_0_0m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Distance_from_L1", "Depth_m", "Domain"))
Sum_Comm_0_0m_df 

#Create plot
Comm_0_0m_plot = ggplot(Sum_Comm_0_0m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum, 
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  ylab("Relative abundance (%)")

Comm_0_0m_plot

Comm_0_0m_plot_pie = Comm_0_0m_plot + coord_polar("y", start = 0)

Comm_0_0m_plot_pie 

```
###14.3km
```{r Community for 14.3 km surface}
#Make combined object
#Fiord_phyloseq_Horonly = merge_phyloseq(Fiord_phyloseq_16S_Horonly, Fiord_phyloseq_18S_Horonly)

#Subset samples
Comm_14.3_0m = subset_samples(Fiord_phyloseq_Horonly, Distance_from_L1 == "14.3" & Sample_Depth == "0" | Distance_from_L1 == "14.3" & Depth_m == "0")

Comm_14.3_0m_df = Comm_14.3_0m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_14.3_0m_df <- summarySE(Comm_14.3_0m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Distance_from_L1", "Depth_m", "Domain"))
Sum_Comm_14.3_0m_df 

#Create plot
Comm_14.3_0m_plot = ggplot(Sum_Comm_14.3_0m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  ylab("Relative abundance (%)")

Comm_14.3_0m_plot

Comm_14.3_0m_plot_pie = Comm_14.3_0m_plot + coord_polar("y", start = 0)

Comm_14.3_0m_plot_pie 


```
##10 m
###0km
```{r Community for 0 km surface}
#Make combined object
#Fiord_phyloseq_Horonly = merge_phyloseq(Fiord_phyloseq_16S_Horonly, Fiord_phyloseq_18S_Horonly)

#Subset samples
Comm_0_10m = subset_samples(Fiord_phyloseq_Horonly, Distance_from_L1 == "0" & Sample_Depth == "10" | Distance_from_L1 == "0" & Depth_m == "10")

Comm_0_10m_df = Comm_0_10m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_0_10m_df <- summarySE(Comm_0_10m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Distance_from_L1", "Depth_m", "Domain"))
Sum_Comm_0_10m_df 

#Create plot
Comm_0_10m_plot = ggplot(Sum_Comm_0_10m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_0_10m_plot

Comm_0_10m_plot_pie = Comm_0_10m_plot + coord_polar("y", start = 0)

Comm_0_10m_plot_pie 

```
###14.3km
```{r Community for 14.3 km surface}
#Make combined object
#Fiord_phyloseq_Horonly = merge_phyloseq(Fiord_phyloseq_16S_Horonly, Fiord_phyloseq_18S_Horonly)

#Subset samples
Comm_14.3_10m = subset_samples(Fiord_phyloseq_Horonly, Distance_from_L1 == "14.3" & Sample_Depth == "10" | Distance_from_L1 == "14.3" & Depth_m == "10")

Comm_14.3_10m_df = Comm_14.3_10m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_14.3_10m_df <- summarySE(Comm_14.3_10m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Distance_from_L1", "Depth_m", "Domain"))
Sum_Comm_14.3_10m_df 

#Create plot
Comm_14.3_10m_plot = ggplot(Sum_Comm_14.3_10m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum, 
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_14.3_10m_plot

Comm_14.3_10m_plot_pie = Comm_14.3_10m_plot + coord_polar("y", start = 0)#+ 
  #geom_text(aes(y = Abundance + c(0, cumsum(Abundance)[-length(Abundance)]), label = percent(Abundance)), size=4)

Comm_14.3_10m_plot_pie 

```
#Vertical
##Surface (0 m)
```{r Community for surface}
#Make combined object
Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_0m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "0" | Depth_m == "0")

Comm_Vert_0m_df = Comm_Vert_0m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_0m_df <- summarySE(Comm_Vert_0m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_0m_df 

#Create plot
Comm_Vert_0m_plot = ggplot(Sum_Comm_Vert_0m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum, 
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_0m_plot

Comm_Vert_0m_plot_pie = Comm_Vert_0m_plot + coord_polar("y", start = 0)
Comm_Vert_0m_plot_pie 

```
##10m
```{r Community for 10m}
#Make combined object
#Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_10m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "10" | Depth_m == "10")

Comm_Vert_10m_df = Comm_Vert_10m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_10m_df <- summarySE(Comm_Vert_10m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_10m_df 

#Create plot
Comm_Vert_10m_plot = ggplot(Sum_Comm_Vert_10m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_10m_plot

Comm_Vert_10m_plot_pie = Comm_Vert_10m_plot + coord_polar("y", start = 0)
Comm_Vert_10m_plot_pie 

```

##40m
```{r Community for 40m}
####Prokaryotes####

#Subset samples
Comm_Vert_40m_Prok = subset_samples(Fiord_phyloseq_16S_Vert, Sample_Depth == "40")

Comm_Vert_40m_Prok_df = Comm_Vert_40m_Prok %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_40m_Prok_df <- summarySE(Comm_Vert_40m_Prok_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth"))
Sum_Comm_Vert_40m_Prok_df 

#Create plot
Comm_Vert_40m_Prok_plot = ggplot(Sum_Comm_Vert_40m_Prok_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_40m_Prok_plot

Comm_Vert_40m_Prok_plot_pie = Comm_Vert_40m_Prok_plot + coord_polar("y", start = 0)

Comm_Vert_40m_Prok_plot_pie 

####Eukaryotes####
#Subset samples
Comm_Vert_40m_Euk = subset_samples(Fiord_phyloseq_18S_Vert, Depth_m == "40")

Comm_Vert_40m_Euk_df = Comm_Vert_40m_Euk %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_40m_Euk_df <- summarySE(Comm_Vert_40m_Euk_df, measurevar="Abundance", groupvars=c("Phylum", "Depth_m"))
Sum_Comm_Vert_40m_Euk_df 

#Create plot
Comm_Vert_40m_Euk_plot = ggplot(Sum_Comm_Vert_40m_Euk_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_40m_Euk_plot

Comm_Vert_40m_Euk_plot_pie = Comm_Vert_40m_Euk_plot + coord_polar("y", start = 0)

Comm_Vert_40m_Euk_plot_pie 
####Combined####
#Make combined object
#Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_40m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "40" | Depth_m == "40")

Comm_Vert_40m_df = Comm_Vert_40m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_40m_df <- summarySE(Comm_Vert_40m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_40m_df 

#Create plot
Comm_Vert_40m_plot = ggplot(Sum_Comm_Vert_40m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_40m_plot

Comm_Vert_40m_plot_pie = Comm_Vert_40m_plot + coord_polar("y", start = 0)
Comm_Vert_40m_plot_pie 

```

##100m
```{r Community for 100m}
#Make combined object
#Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_100m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "100" | Depth_m == "100")

Comm_Vert_100m_df = Comm_Vert_100m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_100m_df <- summarySE(Comm_Vert_100m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_100m_df 

#Create plot
Comm_Vert_100m_plot = ggplot(Sum_Comm_Vert_100m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_100m_plot

Comm_Vert_100m_plot_pie = Comm_Vert_100m_plot + coord_polar("y", start = 0)
Comm_Vert_100m_plot_pie 

```

##200m
```{r Community for 200m}
#Make combined object
#Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_200m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "200" | Depth_m == "200")

Comm_Vert_200m_df = Comm_Vert_200m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_200m_df <- summarySE(Comm_Vert_200m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_200m_df 

#Create plot
Comm_Vert_200m_plot = ggplot(Sum_Comm_Vert_200m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum,
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_200m_plot

Comm_Vert_200m_plot_pie = Comm_Vert_200m_plot + coord_polar("y", start = 0)
Comm_Vert_200m_plot_pie 

```

##360m
```{r Community for 360m}
#Make combined object
#Fiord_phyloseq_Vert = merge_phyloseq(Fiord_phyloseq_16S_Vert, Fiord_phyloseq_18S_Vert)

#Subset samples
Comm_Vert_360m = subset_samples(Fiord_phyloseq_Vert, Sample_Depth == "360" | Depth_m == "360")

Comm_Vert_360m_df = Comm_Vert_360m %>% #Identify the original subsetted phyloseq object
  tax_glom("Phylum") %>% #Merge species with the same Domain.
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Convert the absolute count to a percentage count
  psmelt() %>% #Adjust the data from a phyloseq object into a data.frame-class table  
  filter(Abundance > 0.01)   %>% #Remove samples that make up less than one percent of the abundance.
  arrange(Phylum)#Arange the samples by Domain.

#Make Summary plot
Sum_Comm_Vert_360m_df <- summarySE(Comm_Vert_360m_df, measurevar="Abundance", groupvars=c("Phylum", "Sample_Depth", "Depth_m", "Domain"))
Sum_Comm_Vert_360m_df 

#Create plot
Comm_Vert_360m_plot = ggplot(Sum_Comm_Vert_360m_df,
                          aes(x= "",
                              y=Abundance,
                              fill=Phylum, 
                              group = Domain)) +
  geom_bar(stat = "identity", 
           position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = Phylum_colour_list)+
  #ggtitle("Fjord Sound sample") + 
  #facet_grid("Sample_Depth")+
  #theme(plot.title = element_text(hjust = 0.5))+
  #xlab("Sample Depth (m)")+
  ylab("Relative abundance (%)")

Comm_Vert_360m_plot

Comm_Vert_360m_plot_pie = Comm_Vert_360m_plot + coord_polar("y", start = 0)
Comm_Vert_360m_plot_pie 
```
#Save pdf's
```{r}
pdf("/My/Path/Combined_col.pdf")
Comm_0_0m_plot_pie + ggtitle("Comm_0_0m")
Comm_0_10m_plot_pie + ggtitle("Comm_0_10m")
Comm_14.3_0m_plot_pie + ggtitle("Comm_14.3_0m")
Comm_14.3_10m_plot_pie + ggtitle("Comm_14.3_10m")
Comm_Vert_0m_plot_pie + ggtitle("Comm_Vert_0m")
Comm_Vert_10m_plot_pie + ggtitle("Comm_Vert_10m")
Comm_Vert_40m_plot_pie + ggtitle("Comm_Vert_40m")
Comm_Vert_100m_plot_pie + ggtitle("Comm_Vert_100m")
Comm_Vert_200m_plot_pie + ggtitle("Comm_Vert_200m")
Comm_Vert_360m_plot_pie + ggtitle("Comm_Vert_360m")
dev.off()
```
Subsequent editing was done within Inkscape.
