---
title: "α-Diversity and Kruskal Wallis tests"
author: "Sven"
date: "2/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Notes:
It is best to go through each dataset (consensus fjord/horizontal Long Sound community/ Vertical Long Sound community) one by one. So following the order of this file from start to finish, in order.

#Set up
```{r Load packages}
library(vegan)
library(phyloseq)
library(ggplot2)
library(dplyr)
library(microbiome)
```
##Import files:
```{r Set path}

uzdir <- "/Users/sven/Desktop/Project_R_analysis/"
otutable_biom_file <- paste("/Users/sven/Desktop/Project_R_analysis/", "Merged_otu_table_json.biom", sep = "")
map_file <- paste("/Users/sven/Desktop/Project_R_analysis/Sorted_out/", "Modified_mapping_file_mod_with_names_and_variables.txt", sep = "")


```
```{r Create phyloseq object}
# Now import the .biom-formatted otu_table-tax_table file.

biom_otu_tax <- import_biom(otutable_biom_file)

# Add sample data to the dataset using merge
bmsd <- import_qiime_sample_data(map_file)
class(bmsd)
dim(bmsd)
sample_data(bmsd)
sample_variables(bmsd)
biom_otu_tax


#Merge into phyloseq format
Fiord_phyloseq <- merge_phyloseq(biom_otu_tax, bmsd)
Fiord_phyloseq
sample_sums(Fiord_phyloseq)

#Save original phyloseq file
Fiord_phyloseq_v = Fiord_phyloseq

#Fix Misslabel
Fiord_phyloseq@sam_data$Sample_Depth[Fiord_phyloseq@sam_data$Sample_Depth == 1] = 0
#Ensure sample depth is seen as a factor for ease of use
sample_data(Fiord_phyloseq)$Sample_Depth<-as.factor(sample_data(Fiord_phyloseq)$Sample_Depth)
```
##Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, function(x) x/10)
sample_sums(Fiord_phyloseq)
```
#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, round)
sample_sums(Fiord_phyloseq)
Fiord_phyloseq = prune_samples(sample_sums(Fiord_phyloseq)>=1, Fiord_phyloseq)
sample_sums(Fiord_phyloseq)
```
Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)
```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq) > 0)
any(taxa_sums(Fiord_phyloseq)== 0)
sum(taxa_sums(Fiord_phyloseq) == 0)
any(taxa_sums(Fiord_phyloseq) > 1)
sum(taxa_sums(Fiord_phyloseq) > 1)
any(taxa_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```
####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq = prune_taxa(taxa_sums(Fiord_phyloseq) > 1, Fiord_phyloseq)
any(sample_sums(Fiord_phyloseq) == 0)
any(sample_sums(Fiord_phyloseq) > 0)
sum(taxa_sums(Fiord_phyloseq) > 0)
any(sample_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```
##Compare sequences per sample or OTU
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq),TRUE), sorted = 1:ntaxa(Fiord_phyloseq), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq),TRUE),sorted = 1:nsamples(Fiord_phyloseq), type = "Samples"))

title = "Total number of reads"

p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```
```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq)
```
```{r Attached OTU ID}
tax_table(Fiord_phyloseq) <- cbind(tax_table(Fiord_phyloseq), OTU=taxa_names(Fiord_phyloseq))
```
```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq) =gsub("D_0__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_1__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_2__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_3__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_4__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_5__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_6__", "", tax_table(Fiord_phyloseq))

```
#Subset phyloseq objects
```{r Subset}
#Subset to in/out
Fiord_phyloseq_in_out = subset_samples(Fiord_phyloseq, !Sample_type == "Transverse")

#Subset horizontal community
Fiord_phyloseq_Horonly = subset_samples(Fiord_phyloseq, Sample_type == "Transverse" & !Sample_Depth == "40" & !Sample_Depth == "100" & !Sample_Depth == "200" & !Sample_Depth == "360")

#Subset vertical community
Fiord_phyloseq_Vert = subset_samples(Fiord_phyloseq, !Sample_type == "in" & !Sample_type == "out")
Fiord_phyloseq_Vert = subset_samples(Fiord_phyloseq_Vert, Sample_Site == "L5")
```


##Phylum colour list for consistency
```{r Phylum colour list}
Phylum_colour_list = c(Acidobacteria = "red",
                       Actinobacteria = "green",
                       "Alphaproteobacteria" = "burlywood1",
                       "Alveolata" = "blueviolet",
                       Archaeplastida = "#F8766D",
                       Bacteroidetes = "steelblue",  
                       Chlamydiae = "navy", 
                       Chloroflexi = "grey",
                       Cyanobacteria = "purple", 
                       "Deltaproteobacteria" = "orange",
                       "Discoba" = "darkslategray1",
                       Euryarchaeota = "aquamarine", 
                       "Epsilonproteobacteria" = "darkslateblue",
                       "Excavata" = "#7CAE00",
                       "Gammaproteobacteria" = "dimgray",
                       "Holozoa" = "forestgreen",
                       "Marine Group I" = "gainsboro",
                       Marinimicrobia = "darkseagreen1",
                       Opisthokonta = "magenta", 
                       Parcubacteria = "chocolate2", 
                       Planctomycetes = "wheat", 
                       Proteobacteria = "olivedrab",
                       "Rhizaria" = "goldenrod",
                       Thaumarchaeota = "firebrick", 
                       SAR = "darkred", 
                       "Stramenopiles" = "darkorchid1",
                       "Thermoplasmata" = "tan",
                       Verrucomicrobia = "gold4", 
                       "Rare Taxa (<1%)" = "black")
```
#Consensus fjord α-diversity plot
```{r Consensus plot set up and plotting}
#Carry out richness calculations
alpha_summary_in_out <- estimate_richness(Fiord_phyloseq_in_out, measures = c("Observed", "Shannon"))
Evenness_in_out <- evenness(Fiord_phyloseq_in_out, 'pielou')
alpha_summary_in_out$Pielou <- Evenness_in_out$pielou
#combine with metadata
alpha_meta_in_out <- data.frame(alpha_summary_in_out, sample_data(Fiord_phyloseq_in_out))
alpha_meta_in_out

#Count how many depth levels there are - should be two
levels(alpha_meta_in_out$Sample_Depth)

#Relabell depth levels
levels(alpha_meta_in_out$Sample_Depth) = c("0 m", "10 m")

#Make a manual fjord name list
Fjordlist = c("Breaksea Sound", "Chalky Inlet", "Doubtful Sound", "Dusky Sound", "Wet Jacket Arm")

#Carry out plotting
Observed_Richness_in_out_D <- ggplot(alpha_meta_in_out, aes(x=Sample_Site, y=Observed)) + 
  geom_point(size=1, aes(colour=Sample_type)) +
  geom_smooth(method = "lm") +         
  xlab("Fjord") +
 # ggtitle("In and out samples separated by depth (metre)") +
  labs(y = expression ("Observed Richness")) +
  expand_limits(y=0) +                        
  theme_bw() +
  facet_wrap(~Sample_Depth) +
#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  #theme(axis.title.x = element_text(size=30),
#        axis.text.x = element_text(angle=0, colour = "black", vjust=1, hjust = 0.5, size=30), 
 #       axis.text.y = element_text(colour = "black", size=30),
  #      axis.title.y = element_text(face="bold",size=30),
   #     plot.title = element_text(size = 30,hjust=0.5),
    #    legend.title =element_text(size = 30),
     #   legend.text = element_text(size = 28),
      #  legend.position="right",
       # legend.key.size = unit(1, "cm"),
      #  strip.text.x = element_text(size=30, face="bold"),
       # strip.text.y = element_text(size=30, face="bold"),
        #panel.background = element_blank(),
        #panel.border = element_rect(fill = NA, colour = "black"),
       # strip.background = element_rect(colour="black"))+
  labs(colour = "Sample region", title = element_blank())+
  scale_colour_manual(labels = c("Inner", "Outer"), values = c("red", "blue"))+
  scale_x_discrete(labels = Fjordlist)+
  theme(axis.text.x=element_text(color = "black", angle=45, vjust=.8, hjust=0.8))

```
```{r Export consensus fjords for later ggarrange}
saveRDS(Observed_Richness_in_out_D,"~/Desktop/Multifjord_alphaDiv_16S.rds")
```
#Consensus fjord Kruskal-Wallis (KW) tests
```{r Carry out consensus KW tests}
kruskal.test(Observed ~ Sample_type, data = alpha_meta_in_out)
kruskal.test(Observed ~ Sample_Site, data = alpha_meta_in_out)
kruskal.test(Observed ~ Sample_Depth, data = alpha_meta_in_out)

kruskal.test(Shannon ~ Sample_type, data = alpha_meta_in_out)
kruskal.test(Shannon ~ Sample_Site, data = alpha_meta_in_out)
kruskal.test(Shannon ~ Sample_Depth, data = alpha_meta_in_out)
```
#Horizontal community α-diversity plot
```{r Horizontal community plot set up and plotting}
#Calculate richness
alpha_summary_Hor <- estimate_richness(Fiord_phyloseq_Hor, measures = c("Observed", "Shannon"))
Evenness_Hor <- evenness(Fiord_phyloseq_Hor, 'pielou')
alpha_summary_Hor$Pielou <- Evenness_Hor$pielou
#combine with metadata
alpha_meta_Hor <- data.frame(alpha_summary_Hor, sample_data(Fiord_phyloseq_Hor))
alpha_meta_Hor

#Add distance from L1 onto df
observedrichness_distancefrom_L1 = alpha_meta_Hor[,-c(51:86)]

observedrichness_distancefrom_L1$Distancefrom_L1 = as.numeric("0")

observedrichness_distancefrom_L1[1,51] = 14.3
observedrichness_distancefrom_L1[2,51] = 8.47
observedrichness_distancefrom_L1[3,51] = 8.47
observedrichness_distancefrom_L1[4,51] = 5.59
observedrichness_distancefrom_L1[5,51] = 10.67
observedrichness_distancefrom_L1[6,51] = 14.3
observedrichness_distancefrom_L1[7,51] = 14.3
observedrichness_distancefrom_L1[8,51] = 14.3
observedrichness_distancefrom_L1[9,51] = 0
observedrichness_distancefrom_L1[10,51] = 8.47
observedrichness_distancefrom_L1[11,51] = 2.47
observedrichness_distancefrom_L1[12,51] = 8.47
observedrichness_distancefrom_L1[13,51] = 3.16
observedrichness_distancefrom_L1[14,51] = 4.73
observedrichness_distancefrom_L1[15,51] = 10.67
observedrichness_distancefrom_L1[16,51] = 0
observedrichness_distancefrom_L1[17,51] = 5.59
observedrichness_distancefrom_L1[18,51] = 0
observedrichness_distancefrom_L1[19,51] = 4.73
observedrichness_distancefrom_L1[20,51] = 5.59
observedrichness_distancefrom_L1[21,51] = 5.59
observedrichness_distancefrom_L1[22,51] = 3.17
observedrichness_distancefrom_L1[23,51] = 0

#Change facet wrap labels
observedrichness_distancefrom_L1$Sample_Depth = as.factor(observedrichness_distancefrom_L1$Sample_Depth)

levels(observedrichness_distancefrom_L1$Sample_Depth)
levels(observedrichness_distancefrom_L1$Sample_Depth) = c("0 m", "10 m")

#Make plot
Observed_Richness_Hor_D_distance <- ggplot(observedrichness_distancefrom_L1, aes(x=Distancefrom_L1, y=Observed)) + 
  geom_point(size=3.5) +
  geom_smooth(method = "lm") +         
  xlab("Sample site") +
  #ggtitle("Sample observed richness separated by depth") +
  labs(y = expression ("Observed Richness")) +
  xlab("Distance from outermost sample (km)")+
  expand_limits(y=0) +                        
  theme_bw() +
  facet_wrap(~Sample_Depth) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(axis.title.x = element_text(),
        axis.text.x = element_text(angle=0, colour = "black", hjust = 0.5), 
        axis.text.y = element_text(colour = "black"),
        axis.title.y = element_text(face="bold"),
        plot.title = element_text(hjust=0.5),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black"),
        strip.background = element_rect(colour="black"))

```
```{r Export Horizontal community for later ggarrange}
saveRDS(Observed_Richness_Hor_D_distance,"~/Desktop/Transect_alphadiv_16S_Observed.rds")
```
#Horizontal community Kruskal-Wallis (KW) tests
```{r Carry out horizontal community KW tests}

#Add distances to the phyloseq object for accuracy (rather than using stations)
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L1"] = 0
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L2"] = 5.59
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L3"] = 14.3
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L4"] = 10.67
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L5"] = 8.47
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L6"] = 4.73
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L7"] = 3.16
alpha_meta_Hor$Distance[alpha_meta_Hor$Sample_Site == "L8"] = 2.47

kruskal.test(Observed ~ Distance, data = alpha_meta_Hor) #This means that the alpha-diversity seems to change as we go along the Fjord.
#0.0349

kruskal.test(Observed ~ Sample_Depth, data = alpha_meta_Hor) #No significance.
#0.4777

```
#Vertical community α-diversity plot
```{r Vertical community plot set up and plotting}

#Calculate richness
alpha_summary_Vert <- estimate_richness(Fiord_phyloseq_Vert, measures = c("Observed", "Shannon"))
Evenness_Vert <- evenness(Fiord_phyloseq_Vert, 'pielou')
alpha_summary_Vert$Pielou <- Evenness_Vert$pielou
#combine with metadata
alpha_meta_Vert <- data.frame(alpha_summary_Vert, sample_data(Fiord_phyloseq_Vert))
alpha_meta_Vert

#Make summary
Observed_summary = summarySE(alpha_meta_Vert, "Observed", groupvars = "Sample_Depth")

#Make plot
Observed_Richness_Vert_D <- ggplot(Observed_summary, 
                                   aes(x=as.factor(as.numeric(as.character(Sample_Depth))), 
                                       y=Observed)) + 
  geom_line(group = "Sample_Depth")+
  labs(y = expression ("Observed Richness"), x = expression("Sample Depth (m)")) +
  expand_limits(y=0) +                        
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  #coord_flip()+
 # scale_x_reverse()+
  geom_errorbar(aes(ymin = Observed-se, ymax = Observed + se))

```
```{r Export Vertical community for later ggarrange}
saveRDS(Observed_Richness_Vert_D,"~/Desktop/Profile_alphadiv_16S_Observed.rds")
```
#Vertical community Kruskal-Wallis (KW) tests
```{r Carry out vertical community KW tests}
kruskal.test(Observed ~ Sample_Depth, data = alpha_meta_Vert)


```


